%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% -------------- README --------------
% Visit https://github.com/vgnshiyer/ASU-sparkysundevil-resume-template for comprehensive documenation.

% -------------- Resume ---------------
\documentclass{resume}

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={pranali khedekar},
    email={pranali95khedekar@gmail.com},
    phone={9657709491},
    linkedin={https://www.linkedin.com/in/pranali-khedekar-7bb5081bb/},
    github={}
]

% --------- Summary -----------
\summary{Currently associated with D.D.E. Pune (Pharma) as an Automation engineer with having Technical strong knowledge of 2 years in Instrumentation, Control systems, Industrial Automation, and Electrical systems.Seeking a responsible and challenging position with a turbulent and dynamic organization that offers opportunities for personal and professional development, and where I can best utilize my knowledge and skills. }

% --------- Education ---------
\begin{educationSection}{Education}
    \educationItem[
        university={Savitribai Phule Pune University},
        college={AISSMS College of engineering-Pune},
        graduation={May 2021},
        grade={70 percentage},
        program={B.S.E., Mechanical Engineering},
        coursework={PLC, SCADA, VFD, of Siemens, Allen Bradley, Mitsubishi},
    ]
\end{educationSection}

% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={},
        skills={ Preparation of IO List, System Architecture, Cable Schedule, Project Schedule, BOM, Hardware design specification (HDS), Software Design Specifications (SDS).
\item  PLC Logic Modification. HMI/SCADA Modification. 
3. Control panel testing, Pre-FAT, FAT, SAT. Erection & Site commissioning. 
4. Selection, Testing, Installation, Termination, Settings, Calibration, and commissioning of Field instruments, PID Controllers, PLC and DCS Systems.
5. Selection, Installation and Development of DCS, SCADA, PLC, and HMI software.
6. Troubleshooting of Field Instruments, PLC control panels, MCC Control panels, PLC, HMI, SCADA, DCS systems, and solutions for same.
7. Preparation and Review of Techno commercial offers & Vendor package documents. Designing of PLC and MCC Panels.
8. IO Testing, Audit Trail Reports, Alarm Reports, and Process Reports. Access level checking, Password policies checking as per 21 CFR part 11 Compliance. FAT Protocols fill-ups.
9. Knowledge of Multiple Effect Evaporation, Distillery, CIP, SIP, Boiler, Turbine, Milling, Fermentation, Distillation and Dryer Processes.
10. On-site training to Operation & Maintenance engineers & team during SAT.
11. Operation and Maintenance work of Industrial automation system. Preventive and Breakdown maintenance.
12. PLC: Allen Bradley, ABB, Siemens PLC.
13. DCS: HollySys.
14. SOFTWARES: RS Logix500, RS Logix5000, Studio5000, Factory Talk View ME, Factory Talk View SE, Basics of SQL, Automation Builder, CodeSys, InduSoft Web Studio, TIA Portal, Proposal Works, Integrated Architecture Builder (IAB), MS Office, ERP.}
    ] \\
    \skillItem[
        category={Design and Modeling Tools},
        skills={ LabVIEW, MATLAB, Microsoft Office}
    ] \\
    \skillItem[
        category={Programming},
        skills={Python, C,}
    ] \\
    \skillItem[
        category={Certifications},
        skills={PLC and SCADA from Softcon Institute, 
        Matlab from Pantech Institute, Machine learning from Verseo Institute}
    ]
\end{skillsSection}

% --------- Experience -----------
\begin{experienceSection}{Professional Experience}
    \experienceItem[
        company={DD Enterprises},
        location={Bhosari,Pune},
        position={Automation Engineer (2 years)},
        duration={Feb 2022 – 2024}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item  Preparing and finalizing the design of system architecture, reviewing IO count, validating the use of high-ended software (Historian, FFTM, Assetcenter, Redundancy, Virtual machine).Experience in 3rd party integrations. Performing Prefat, FAT loop verification, IO testing, and calibrations.
        \item Good knowledge of 21 CFR part 11 compliance, GAMP-5, ISA88, P&ID, PFDs,FDS, VM, cost optimization. 
        \item Preparing automation philosophy and costing of all projects for Technical sales and support and making a profit of 1.50 Cr.
    \end{itemize}

    

\end{experienceSection}

% --------- Projects -----------
\begin{experienceSection}{Academic projects}
    \projectItem[
        title={1.800L CIP/SIP VESSELS WITH 21 CFR PART 11 COMPLIANCE },
        duration={2022 – 2022},
        keyHighlight=
{Client Name:}{ Egyptian International Pharma Industries (EIPICO), Egypt. 

}
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item PLC: Siemens S7 1500, Software: TIA Portal V15.1, VFD: Siemens, Field Instruments: Emerson, Radix, Gemu, SMC
    \end{itemize}

    \projectItem[
        title=Sensor for Quadriplegic Patients,
        duration=Spring 2019,
        keyHighlight=Led team of three to design and develop a mouse-like device to allow quadriplegic patients to use websites.
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Assessed range-of-motion data to determine feasible solutions (Python)
        \item Created device to detect muscle flexion in neck to control the mouse click (Arduino, FPGA)
    \end{itemize}
\end{experienceSection}

% --------- Other work experience -----------
\begin{experienceSection}{Other work experience}
    \experienceItem[
        company={Arizona State University},
        location={Tempe, AZ},
        position={Tutor (10 hours/week)},
        duration={Aug 2018 – May 2019}
    ]
    \begin{itemize}
        \vspace{-0.2em}
        \itemsep -6pt {}
        \item Tutored 10-15 undergraduate engineering students per week in MATLAB programming and math coursework
    \end{itemize}

    \experienceItem[
        company={Kohl's},
        location={Gilbert, AZ},
        position={Sales Associate, Jewelry Department (16-24 hours/week)},
        duration={Aug 2017 – Dec 2017}
    ]
    \begin{itemize}
        \vspace{-0.2em}
        \itemsep -6pt {}
        \item Achieved \#2 highest selling associate within one month of hire date
    \end{itemize}
\end{experienceSection}

% --------- Activities -----------
\begin{experienceSection}{Activities}
    \projectItem[
        title={ASU Society of Women Engineers (SWE)},
        keyHighlight={Multiple leadership roles, including vice-president and industry relations chair (300 members{,} \$75k annual budget)},
        duration={Aug 2017 – Present}
    ]
    \begin{itemize}
        \vspace{-0.5em}
        \itemsep -6pt {}
        \item Tutored 10-15 undergraduate engineering students per week in MATLAB programming and math coursework
        \item Organized 2018 annual conference participation, including 8 student poster submissions
    \end{itemize}
\end{experienceSection}

\end{document}

